---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# treepac

<!-- badges: start -->
<!-- badges: end -->

`treepac` is a collection of 3 functions (and a demonstration dataset) aimed to streamline repetitive tasks in exploratory data analyses, so users can quickly arrive at meaningful conclusions from their data.

## Installation

You can install the development version of treepac from [GitHub](https://github.com/) with:

``` r
install.packages("remotes")
install.packages("devtools")
devtools::install_github("ADC-405-S26/treepac")
```

Once you have installed the package, remember to invoke it in your environment:

```{r setup}
library(treepac)
```


## Examples

This section contains some examples of what you can do with the provided functions:

* `llreg()`
* `pctchg()`
* `theme_3pac()`

### `llreg`

This function is supposed to show the elasticity between 2 variables (in other words, the linear relationship between the natural log of y and the natural log of x):

```{r}
# the function takes 3 arguments
# treedat is the package's dataset
# remember to pass the column names in quotes!
llreg(treedat, "x", "y")
```

### `pctchg`

This function takes 2 arguments, a dataframe, and a numeric column within it and returns an additional column that shows the entry-to-entry percentage changes of the target column:

```{r}
treedatgr <- pctchg(treedat, 'x')
# the output df contains an additional column:
# pctchg_x
head(treedatgr, 6)

```

### `theme_3pac()`
This is a ggplot2 theme based off of `theme_bw()`. Atop the theme, a few changes were made to improve visual clarity and legibility:

```{r}
library(ggplot2)

ggplot(data = treedat, aes(x = x, y = y, col = z)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(title = 'Example scatter with spline fitting',
       subtitle = 'theme_3pac() example',
       caption = 'Data were randomly generated and are not reflective of any real-life trend') +
  theme_3pac()
```

